Evaluation of probabilistic photometric redshift estimation approaches for \boldblue{ \textsc{The Rubin Observatory Legacy Survey of Space and Time} (LSST)}

### 2020-03-14 paper/tex/appendix.tex
add final bootstrap fig update

Figure~\ref{fig:nz_stats} shows the quantitative Kolmogorov-Smirnoff (KS), Cramer-Von Mises (CvM), and Anderson Darling (AD) test statistics for each of the codes for the $\hat{N}(z)$ based measures.
The horizontal lines show the the result of a bootstrap resampling of the training set using 30,000 samples for \trainz, representing a conservative idealized limit on expected performance for a modest-sized representative training set of galaxies, as mentioned in Section~\ref{sec:pitqq}.
The AD bootstrap statistic is elevated due to its sensitivity to the tails of distributions.
The stacked estimators of the redshift distribution for \cmnn\ and \trainz\ best estimate $\tilde{N}(z)$ under these metrics, whereas \eazy, \lephare, \metaphor, and \skynet\ underperform; \bpz, \gpz, and \tpz\ are within a factor of two of the conservative limit for all statistics.
It is unsurprising that \cmnn\ scores well, as with a nearly complete and representative training set choosing neighbouring points in colour/magnitude space to construct an estimator should lead to excellent agreement in the final $\hat{N}(z)$.

\begin{figure*}
\centering
\includegraphics[width=0.74\textwidth]{fig/KSvsCvMvsAD_NZ_withnull_jpg.jpg}
\caption{A visualization of the Kolmogorov-Smirnoff (KS, blue diamond), Cramer-von Mises (CvM, black star), and Anderson-Darling (AD, red asterisk) statistics for the $\hat{N}(z)$ distributions.
Horizontal lines indicate the statistic values (including uncertainty) achieved using \trainz\ via bootstrap resampling a training set containing 30,000 redshifts.
We make the reassuring observation that these related statistics do not disagree significantly with one another.
\cmnn\ outperforms the control case, \trainz, and several codes are within a factor of two of this conservative idealized limit.
\skynet\ scores poorly due to an overall bias in its redshift predictions.}
\label{fig:nz_stats}
\end{figure*}

>>>>

Figure~\ref{fig:nz_stats} shows the quantitative Kolmogorov-Smirnoff (KS), Cramer-Von Mises (CvM), and Anderson Darling (AD) test statistics for each of the codes for the $\hat{N}(z)$ based measures.
The horizontal lines show the the result of a bootstrap resampling of the training set using \sout{30}\boldblue{44},000 samples for \trainz, representing a conservative \sout{idealized limit on expected performance for a} \boldblue{error estimate assuming our} modest-sized representative training set of galaxies, as mentioned in Section~\ref{sec:pitqq}.
The AD bootstrap statistic is elevated due to its sensitivity to the tails of distributions.
The stacked estimators of the redshift distribution for \cmnn\ and \trainz\ best estimate $\tilde{N}(z)$ under these metrics, whereas \eazy, \lephare, \metaphor, and \skynet\ underperform; \bpz, \gpz, and \tpz\ are within a factor of two of the conservative limit for all statistics.
It is unsurprising that \cmnn\ scores well, as with a nearly complete and representative training set choosing neighbouring points in colour/magnitude space to construct an estimator should lead to excellent agreement in the final $\hat{N}(z)$.

\begin{figure*}
\centering
\includegraphics[width=0.74\textwidth]{fig/KSvsCvMvsAD_NZ_withnull_44k.jpg}
\caption{A visualization of the Kolmogorov-Smirnoff (KS, blue diamond), Cramer-von Mises (CvM, black star), and Anderson-Darling (AD, red asterisk) statistics for the $\hat{N}(z)$ distributions.
Horizontal lines indicate the statistic values (including uncertainty) achieved using \trainz\ via bootstrap resampling a training set containing \sout{30}\boldblue{44},000 redshifts.
We make the reassuring observation that these related statistics do not disagree significantly with one another.
\cmnn\ outperforms the control case, \trainz, and several codes are within a factor of two of this conservative idealized limit.
\skynet\ scores poorly due to an overall bias in its redshift predictions.}
\label{fig:nz_stats}
\end{figure*}
